Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction

### 2024-03-11 paper/remotesensing-2870812-english.tex

\begin{figure}[H]
\vspace{-0.1in}
\hspace{-9pt}\includegraphics[width=0.7\columnwidth]{figures/results/downwelling-hist.pdf}
\vspace{-0.15in}
\caption{\hl{Distribution} %MDPI: Please use commas to separate thousands for numbers with five or more digits (not four digits) in the picture, e.g., "10000" should be "10,000".
 of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

In \cite{robotTeam1}, we introduced this paradigm. In this study, we have built on this approach in three new ways. First, we have demonstrated the ability to effectively combine observations from disparate collections by augmenting the machine learning models with sufficient features describing the illumination and viewing geometries. As Figure~\ref{fig:downwelling-hist} indicates, we observed variation in the total downwelling intensity between the images collected on the same day and between each separate collection period. These within-collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds. Moreover, the assumption that the water's surface can be treated as Lambertian is clearly violated when the water is not perfectly still. Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing angles as additional features in the final dataset.  This fact is reinforced by the position of these variables as the most important features for each of the estimated water quality variables. As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects when combining data from multiple collections.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, \hl{Table S1:} %MDPI: please provide an independent file to indicate supplementary materials.
 Hyperspectral reflectance indices.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, D.J.L.; methodology, \hl{J.W.} %MDPI: We changed all J.L.W. into J.W. Please confirm.
 and D.J.L; software, J.W.; field deployment and preparation, J.W., A.A., L.O.H.W., S.T., B.F., P.M.H.D., M.I., M.L., D.S., and D.J.L.; validation, J.W.; formal analysis, J.W.; investigation J.W.; resources, D.J.L.; data curation, J.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.W.; writing---review and editing, J.W. and D.J.L.; visualization, J.W.; supervision, D.J.L.; project administration, D.J.L.; funding acquisition, D.J.L. All authors have read and agreed to the published version of the manuscript.
}

@@

\bibitem[Lary(2010)]{lary2010artificial}
Lary, D.J.
\newblock Artificial intelligence in geoscience and remote sensing. In {\em
  Geoscience and Remote Sensing New Achievements}; \hl{IntechOpen:} %MDPI: Please add the location of the publisher (City and Country).
  2010.

@@

\bibitem[Kurihara et~al.(2020)Kurihara, Ishida, and
  Takahashi]{kurihara2020unmanned}
Kurihara, J.; Ishida, T.; Takahashi, Y.
\newblock Unmanned Aerial Vehicle (UAV)-based hyperspectral imaging system for
  precision agriculture and forest management.
\newblock In {\em Unmanned Aerial Vehicle: Applications in Agriculture and
  Environment}; \hl{2020} %MDPI: Please add the name of the publisher and their location.
; pp. 25--38.

@@

\bibitem[Tillman(2017)]{tillman2017evaluation}
Tillman, E.F.
\newblock \emph{Evaluation of the Eureka Manta2 Water-Quality Multiprobe Sonde};
\newblock Technical report; \hl{US Geological Survey:} %MDPI: Please add the location of the publisher (City and Country).
  2017.

@@

\bibitem[M{\"u}ller et~al.(2002)M{\"u}ller, Lehner, Muller, Reinartz,
  Schroeder, and Vollmer]{GeorectificationMuller}
M{\"u}ller, R.; Lehner, M.; Muller, R.; Reinartz, P.; Schroeder, M.; Vollmer,
  B.
\newblock \emph{A Program for Direct Georeferencing of Airborne and Spaceborne Line
  Scanner Images};
\newblock  \hl{2002.} %MDPI: Please add the name of the publisher and their location.

@@

\bibitem[Thenkabail et~al.(2018)Thenkabail, Lyon, and
  Huete]{thenkabail2018hyperspectral}
Thenkabail, P.S.; Lyon, J.G.; Huete, A.
\newblock {\em Hyperspectral Indices and Image Classifications for Agriculture
  and Vegetation}; CRC Press:  \hl{Boca Raton, FL, USA,} %We added the location of publisher. Please confirm
 2018.

@@

\bibitem[Breiman(2017)]{decision-trees}
Breiman, L.
\newblock {\em Classification and Regression Trees}; \hl{Routledge:} %MDPI: Please add the location of the publisher (City and Country).
  2017.

@@

\bibitem[Louppe et~al.(2013)Louppe, Wehenkel, Sutera, and
  Geurts]{rfr-importance-ranking}
Louppe, G.; Wehenkel, L.; Sutera, A.; Geurts, P.
\newblock Understanding variable importances in forests of randomized trees.
\newblock {\em Adv. Neural Inf. Process. Syst.} {\bf 2013},
  {\em \hl{26}}.
%MDPI: Please add page.

@@

\bibitem[Papadopoulos(2008)]{conformal-prediction-4}
Papadopoulos, H.
\newblock Inductive conformal prediction: Theory and application to neural
  networks. In {\em Tools in Artificial Intelligence}; \hl{Citeseer:} %MDPI: Please add the location of the publisher (City and Country).
 2008.

>>>>

\begin{figure}[H]
\vspace{-0.1in}
\hspace{-9pt}\includegraphics[width=0.7\columnwidth]{figures/results/downwelling-hist.pdf}
\vspace{-0.15in}
\caption{Distribution of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

In \cite{robotTeam1}, we introduced this paradigm. In this study, we have built on this approach in three new ways. First, we have demonstrated the ability to effectively combine observations from disparate collections by augmenting the machine learning models with sufficient features describing the illumination and viewing geometries. As Figure~\ref{fig:downwelling-hist} indicates, we observed variation in the total downwelling intensity between the images collected on the same day and between each separate collection period. These within-collection variations are due to a combination of the stability of the UAV (on which the upward facing downwelling irradiance spectrometer is mounted) together with the occasional interference of clouds. Moreover, the assumption that the water's surface can be treated as Lambertian is clearly violated when the water is not perfectly still. Despite the potential impact of these limitations on the quality of the resulting reflectance data cubes, the smoothness of the maps generated by our models suggests that we have provided sufficient context by including the relevant solar illumination and viewing angles as additional features in the final dataset.  This fact is reinforced by the position of these variables as the most important features for \textit{each} of the estimated water quality variables. As long as we are primarily interested in these values and not the reflectances themselves, we are able to successfully account for these lighting effects when combining data from multiple collections.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Table S1: %MDPI: please provide an independent file to indicate supplementary materials.
 Hyperspectral reflectance indices.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, D.J.L.; methodology, J.W. and D.J.L; software, J.W.; field deployment and preparation, J.W., A.A., L.O.H.W., S.T., B.F., P.M.H.D., M.I., M.L., D.S., and D.J.L.; validation, J.W.; formal analysis, J.W.; investigation J.W.; resources, D.J.L.; data curation, J.W., A.A., L.O.H.W., and D.J.L; writing---original draft preparation, J.W.; writing---review and editing, J.W. and D.J.L.; visualization, J.W.; supervision, D.J.L.; project administration, D.J.L.; funding acquisition, D.J.L. All authors have read and agreed to the published version of the manuscript.
}

@@

\bibitem[Lary(2010)]{lary2010artificial}
Lary, D.J.
\newblock Artificial intelligence in geoscience and remote sensing. In {\em
  Geoscience and Remote Sensing New Achievements}; IntechOpen: London, United Kingdom,
  2010.

@@

\bibitem[Kurihara et~al.(2020)Kurihara, Ishida, and
  Takahashi]{kurihara2020unmanned}
Kurihara, J.; Ishida, T.; Takahashi, Y.
\newblock Unmanned Aerial Vehicle (UAV)-based hyperspectral imaging system for
  precision agriculture and forest management.
\newblock In {\em Unmanned Aerial Vehicle: Applications in Agriculture and
  Environment}; Springer International Publishing: Cham, Switzerland, 2020 %MDPI: Please add the name of the publisher and their location.
; pp. 25--38.

@@

\bibitem[Tillman(2017)]{tillman2017evaluation}
Tillman, E.F.
\newblock \emph{Evaluation of the Eureka Manta2 Water-Quality Multiprobe Sonde};
\newblock Technical report; US Geological Survey: Reston, VA, United States, %MDPI: Please add the location of the publisher (City and Country).
  2017.

@@

\bibitem[M{\"u}ller et~al.(2002)M{\"u}ller, Lehner, Muller, Reinartz,
  Schroeder, and Vollmer]{GeorectificationMuller}
M{\"u}ller, R.; Lehner, M.; Muller, R.; Reinartz, P.; Schroeder, M.; Vollmer,
  B.
\newblock A Program for Direct Georeferencing of Airborne and Spaceborne Line
  Scanner Images;
\newblock In {\em International Archives of Photogrammetry Remote Sensing and 
  Spatial Information Sciences}; {2002}; pp. 148--153. %MDPI: Please add the name of the publisher and their location.

@@

\bibitem[Thenkabail et~al.(2018)Thenkabail, Lyon, and
  Huete]{thenkabail2018hyperspectral}
Thenkabail, P.S.; Lyon, J.G.; Huete, A.
\newblock {\em Hyperspectral Indices and Image Classifications for Agriculture
  and Vegetation}; CRC Press:  Boca Raton, FL, USA,
 2018.

@@

\bibitem[Breiman(2017)]{decision-trees}
Breiman, L.
\newblock {\em Classification and Regression Trees}; CRC Press: Boca Raton, FL, USA,  %MDPI: Please add the location of the publisher (City and Country).
  2017.

@@

\bibitem[Louppe et~al.(2013)Louppe, Wehenkel, Sutera, and
  Geurts]{rfr-importance-ranking}
Louppe, G.; Wehenkel, L.; Sutera, A.; Geurts, P.
\newblock Understanding variable importances in forests of randomized trees.
\newblock {\em Adv. Neural Inf. Process. Syst.} {\bf 2013},
  {\em 26}, ~431--439.

@@

\bibitem[Papadopoulos(2008)]{conformal-prediction-4}
Papadopoulos, H.
\newblock Inductive conformal prediction: Theory and application to neural
  networks. In {\em Tools in Artificial Intelligence}; IntechOpen: London, United Kingdom %MDPI: Please add the location of the publisher (City and Country).
 2008.
